There are no small Advantages: Reinforcement learning in near continuous time with Deep RelAtive Mixture of Advantages

### 2019-01-15 paper/icml_drau/icml_drau.tex
working with CT

\begin{abstract}
	Despite remarkable successes, \emph{Deep Reinforcement learning} remains sensitive to
	hyperparameterization, implementation details and small environment changes~(\citealt{drl_matter}, \citealt{drl_matter_bis}). 
	Overcoming this sensitivity is key to making DRL applicable to real world problems.
	In this paper, we study the sensitivity of Deep Reinforcement learning algorithms to
	time discretization. More precisely, we show that approaches based on estimations of the
	Q-function, e.g. \emph{Deep Q-learning}~\cite{dqn} and \emph{Deep deterministic policy gradient}~\cite{ddpg}
	are sensitive to variations of time discretization. We further show that a simple reparameterization of the
	Q-function as a sum of a state value term and a \emph{small} action dependent advantage term yields an algorithm
	much more resilient to variations of time discretization.
\end{abstract}

>>>>

\begin{abstract}
	Despite remarkable successes, \emph{Deep Reinforcement learning} (DRL) remains sensitive to
	hyperparameterization, implementation details and small environment changes~(\citealt{drl_matter}, \citealt{drl_matter_bis}). 
	Overcoming this sensitivity is key to making DRL applicable to real world problems.
	In this paper, we study the sensitivity of DRL to
	time discretization in \emph{near continuous time} environments. More precisely, we show that approaches based on estimations of the
	Q-function, e.g. \emph{Deep Q-learning}~\cite{dqn} and \emph{Deep deterministic policy gradient}~\cite{ddpg}
	are sensitive to variations of time discretization.
        We detail a principled method to obtain an off-policy RL algorithm that is more robust to changes in time discretization, and demontrate this robustness empirically. 
        % We further show that a simple reparameterization of the
	% Q-function as a sum of a state value term and a \emph{small} action dependent advantage term yields an algorithm
	% much more resilient to variations of time discretization.\LB{Change last sentence to: We introduce a more resilient algorithm to variations of time discretization [We could say more, but still less that what is already there]}
\end{abstract}

### 2019-01-15 paper/icml_drau/intro.tex
working with CT

\section{Introduction}
\label{sec:intro}
In recent years, deep learning based approaches to reinforcement learning have
thrived and provided impressive results in a variety of domains, achieving superhuman
performances with no expert knowledge in perfect information zero-sum
games~\cite{alphazero}, reaching level of top players in video
games~(\citealt{openai_five}, \citealt{dqn}), or learning dexterous manipulation
from scratch without demonstrations~\cite{hand_control}.

In spite of those successes, \emph{Deep reinforcement learning} approaches are
sensitive to a number of factors, including hyperparameterization,
implementation details or small changes in the environment
parameters~(\citealt{drl_matter}, \citealt{drl_matter_bis}). This sensitivity,
along with sample inefficiency, prevents DRL from being applied in most real
world settings. High sensitivity to environment parameters notably prevents
transfering abilities from imperfect simulators to real world scenarios.

In this paper we focus our attention on the sensitivity to time discretization
of DRL approaches, i.e. what happens when an agent receives $50$ observations
and is expected to take $50$ actions per second instead of $10$. One expects
that decreasing time discretization, or equivalently shortening reaction time,
should only improve agent performances. This is not what happens in practice
for approaches based on estimation of state action value functions, e.g.
\emph{Deep Q-learning} (DQN~\citep{dqn} and \emph{Deep deterministic policy
gradient} (DDPG~\citep{ddpg}). This is shown experimentally in Sec.~\ref{sec:exp}.

We relate this sensitivity to the fact that, as the discretization timestep
decreases, the effect of individual actions on the total return decreases, and
can vanish when the discretization timestep becomes infinitesimal. The natural
framework to study this phenomenon is Continuous time reinforcement learning 
(Sec.~\ref{sec:continous}).

To cope for this effect, we introduce a
parameterization of the Q-function as a sum of a state value term and a
\emph{small} action dependent advantage term (Sec.~\ref{subsec:reparam}). This
reparameterized Q approximation can be trained with deep variants of Q-learning
(Sec.~\ref{subsec:algorithm}).  To properly scale w.r.t. time discretization,
particular attention has to be taken regarding both the exploration method, and
the scaling of learning rates (Sec.~\ref{subsec:lr}, Sec.~\ref{subsec:explo}).
The resulting algorithm is shown to provide near perfect invariance to time
discretization on simple environments, and much better invariance properties
than vanilla DQN or DDPG on more complex environments (Sec.~\ref{sec:exp}).

>>>>

%! TEX root = icml_drau.tex

\section{Introduction}
\label{sec:intro}
In recent years, \emph{Deep Reinforcement Learning} (DRL) approaches have
thrived and provided impressive results in a variety of domains, achieving superhuman
performances with no expert knowledge in perfect information zero-sum
games~\cite{alphazero}, reaching level of top players in video
games~(\citealt{openai_five}, \citealt{dqn}), or learning dexterous manipulation
from scratch without demonstrations~\cite{hand_control}. 
In spite of those successes, DRL approaches are
sensitive to a number of factors, including hyperparameterization,
implementation details or small changes in the environment
parameters~(\citealt{drl_matter}, \citealt{drl_matter_bis}). This sensitivity,
along with sample inefficiency, prevents DRL from being applied in most real
world settings. High sensitivity to environment parameters notably prevents
transfering abilities from imperfect simulators to real world scenarios.

In this paper we focus our attention on the sensitivity to time discretization
of DRL approaches,
i.e. what happens when an agent receives $50$ observations
and is expected to take $50$ actions per second instead of $10$. One expects
that decreasing time discretization, or equivalently shortening reaction time,
should only improve agent performances. Robustness to time discretization is notably relevant in \emph{near-continuous}
environments, which includes most continuous control environments, robotics and many video games.
\TODO{Explain that it also includes $\gamma \rightarrow 1$.}

In practice, standard approaches based on estimation of state action value functions, e.g.
\emph{Deep Q-learning} (DQN~\citep{dqn} and \emph{Deep deterministic policy
gradient} (DDPG~\citep{ddpg}) are not robust to changes in time discretization. This is shown experimentally in Sec.~\ref{sec:exp}. 
This sensitivity can be understood as follows: as the discretization timestep
decreases, the effect of individual actions on the total return decreases too, and
can vanish when the discretization timestep becomes infinitesimal. The natural
framework to study this phenomenon is Continuous time reinforcement learning 
(Sec.~\ref{sec:framework}) \cite{cont_rl, adv_upd}.

A time discretization invariant algorithm should
in particular admit a time continuous limit i.\,e. when the discretization timestep goes to $0$.
This leads to precise design choices in term of
agent architecture, exploration policy and learning rates scalings.
The resulting algorithm is shown to provide near perfect invariance to time
discretization on simple environments, and much better invariance properties
than vanilla DQN or DDPG on more complex environments (Sec.~\ref{sec:exp}).
On a new environment, as soon as the order of magnitude of the time discretization is known, our analysis readily provides salient scalings for a number of hyperparameters.

Our contribution is threefold:
\begin{itemize} 
\item We formally show that the Q-function collapses to the V-function in \emph{near-continuous} time, and thus that
    standard Q-learning is ill-behaved in this setting.
  \item Our analysis of limit properties in near continuous environments leads us to define a robust methods off-policy algorithm. In particular,
    it provides insights on how to design architectures, how to explore, and how to scale learning rates.
  \item We empirically show that standard Q-learning methods are not robust to changes in time discretization, and that our algorithm provides huge gain in that domain.
\end{itemize}
